---
title: "Lab 3: Introduction to ggplot"
author: "Hiba Chaudhry"
date: "`4/5/2021`"
output: github_document
---

> This is Lab 3 of Quant Bio. 

Welcome to my Lab 3 repository for Quantitative Biology BIOL 275 at MSUM.

## Lab objectives

The objectives of this lab are:

Use the layered grammar of graphics:

Create a blank graph using the ggplot() function
  Add geometric objects to a graph
  Define an aesthetic mapping for a graph
  Add labels to a graph
  Fix some common styling
  
Create a graph showing the distribution of a single variable
  Create a bar chart for a categorical variable using the geom_col() and geom_bar() functions
  Arrange the categories in a bar chart by frequency
  Create a histogram for a numerical variable using the geom_histogram() function
  Choose and set appropriate histogram bin widths
  
Set the image width for an R Markdown code chunk

## Repository contents

The repository contains the following scripts:

- [Lab Report 3](lab-report.md)








```{r}
# load packages -----------------------------------------------------------
#install.packages(c("nycflights13", "gapminder", "Lahman"))

library(nycflights13)
library(tidyverse)

library(auk)                          # load the auk package
birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa
  
```

#Q1: Print a table containing only species NOT in the Order Passeriformes. Include all columns.
```{r}
filter(birds, order != "Passeriformes")
```

#Q2: Print a table containing only species in the Order Passeriformes. Include all columns.
```{r}
# print a table of passeriformes
#filter(birds, order == "Passeriformes")
```

#Q3:Print a table containing all species. Only the variables Species Code, Scientific Name, and Common Name should be in the final table.
```{r}
select(birds, species_code, scientific_name,common_name)
```

#Q4:Print a table with all species in the Order Passeriformes whose common name starts with the word “Common”. Species should be in reverse taxonomic order (taxon_order variable). Only the variables Species Code, Scientific Name, and Common Name should be in the final table.
```{r}
filter(birds, order == "Passeriformes")
Passeriformes<-filter(birds, order == "Passeriformes") 
filter(Passeriformes, str_detect(common_name, "Common"))
Y<-arrange(Passeriformes,desc(taxon_order))
select(Y, species_code, scientific_name, common_name)
```

#Q5:Print a table containing species with “Warbler” in the common name. Include all columns.
```{r}
# Warbler -----------------------------------------------------------------
Warbler <- filter(birds, str_detect(common_name, "Warbler"))
```

#Q6:Print a table with two columns: family and n, the number of species in that family whose name contains “Warbler”
```{r}
# 2 Columns: Warbler and family  ------------------------------------------
count(Warbler, family)
```



sessioninfo::session_info() 
